Unifying intra- and inter-specific variation in tropical tree mortality

### 2017-12-02 ms/manuscript.Rnw
Minor changes to some text to improve clarity

\documentclass[9pt,twocolumn,twoside]{pnas-new}\usepackage[]{graphicx}\usepackage[]{color}

@@

Another difficulty when studying mortality -- similar to that faced in other fields like medicine and engineering -- is determining the shape of hazard functions that skilfully predict patterns in mortality. Past research has identified a range of factors with significant effects on tree survival, including an individual's growth rate \cite{Kobe:1995tw,Wyckoff:2002ul}, traits \cite{Poorter:2008iu,Kraft:2010kq,Wright:2010fl,AubryKientz:2013dg}, and size \cite{Vieilledent:2010fv, Hurst:2011ky}. However, these influences have not yet been integrated into a common hazard function \cite{Hawkes:2000ib,Zens:2003jv,McDowell:2011dr}.

@@

A further challenge in developing hazard functions for plants is to integrate the conflicting relationships observed within and across species between mortality and growth. Within species, mortality rates are lower for fast-growing individuals, presumably because those individuals have superior carbon budgets and are thus able to tolerate or repair diverse stresses \cite{Kobe:1995tw, Hawkes:2000ib, Keane:2001db}. Empirical studies broadly support this theory, with many indicating exponential declines in mortality with increased growth rate, $X_i(t)$ \cite{Kobe:1995tw, Wyckoff:2000un, Kunstler:2005bn, Vieilledent:2010fv}. By contrast, across species, there is a strong trade-off between growth and survival, with individuals from faster-growing species  exhibiting higher mortality rates than individuals from slower-growing species \cite{Poorter:2008iu, Wright:2010fl}. This trade-off may arise via traits with antagonistic effects, such as wood density. Denser wood -- which is expensive to build and thus slows growth --  reduces stem breakage \cite{vanGelder:2006exa,Chave:2009iy}, embolism \cite{Hacke:2001kj, Jacobsen:2005fx}, pathogen attack \cite{Augspurger:1984wx}, and thereby mortality \cite{Poorter:2008iu, Chave:2009iy, Kraft:2010kq, Wright:2010fl}.

\begin{figure}[!hb]
\centering
\includegraphics{figures/fig1.pdf}
\caption{Outline of methodology.
A) Our data consist of repeat measures of stem diameter ($D$) and status ($S$, 0 = alive or 1 = dead) for individual trees at specific census dates ($t_1$, $t_2$, $t_3$).
B) We consider three alternative hazard functions: 1) a baseline hazard, 2) a growth-dependent hazard; and 3) a function that combines both baseline and growth-dependent hazards. The parameters of the models are biologically interpretable: $\alpha$ defines the instantaneous mortality rate at low growth rate; $\beta$ reflects the sensitivity of mortality rate to changes in growth rate; and $\gamma$ is the asymptote, or baseline hazard. Combined $\alpha$ and $\beta$ capture growth-dependent mortality, while $\gamma$ captures growth-independent mortality (e.g. windfall, fire) that kill a plant, irrespective of its growth rate. For each model form, we consider two alternative predictors of growth, $X$ (basal area and stem diameter growth), as well as allowing for species-level effects on the parameters $\alpha$, $\beta$ and $\gamma$.
C) Each model's skill in predicting observed outcomes ($S$) is quantified via the log-loss function (eq. \ref{eq:logloss}).
D) The predictive skill of alternative models is evaluated via 10-fold cross validation. The entire dataset is split into 10 folds ($F_1$, ..., $F_{10}$). Alternative models were fit 10 times ($M_1$, ..., $M_{10}$), using different combinations of testing and training data. We then average the estimated log loss for each of these 10 model fits.}
\label{fig1}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics{figures/fig2.pdf}
\caption{Comparing predictive skill of alternative hazard functions. Values are mean ($\pm$ 95\% credible intervals) logarithmic loss, with lower values implying greater predictive skill.
A) Five sequential stages of model selection with each stage increasing in complexity. Null: constant ($\gamma$); Census: inclusion of census effects ($\delta_t$); Growth rate: the inclusion of growth rate. This includes two possible hazard functions: growth-dependent only hazard ($(\alpha e^{-\beta X_{i}})\delta_t$) and baseline + growth-dependent hazard with census effects ($(\alpha e^{-\beta X_{i}} + \gamma)\delta_t$); WD: inclusion of wood density effect ($\rho$) on $\gamma$; Species: the inclusion of species random effects $s$ on all parameters.
B) Comparing predictive skill for wood density parameter combinations. Colors represent growth measure used: white = no growth measure, grey = basal area growth, black = dbh growth. For both panels symbols represent functional form: null and growth-independent (circle), growth-dependent hazard (triangle), both growth-independent and growth-dependent hazards (square). Errors in panel A are too small to see.}
\label{fig2}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics{figures/fig3.pdf}
\caption{Relationship between species growth-dependent mortality rate and wood density. Points are estimated mean baseline mortality rates $\pm$ 95\% credible intervals for each of the 203 BCI species used in this study. Blue trendline with grey shading shows average ($\pm$ 95\% credible intervals) expected relationship.}
\label{fig3}
\end{figure}

\subsection*{Wood density and other species effects}
Including wood density as an effect on either growth-independent or growth-dependent parameters significantly improved model skill relative to a model without such effects (Fig. \ref{fig2} A,B). The most parsimonious model, with highest predictive skill, was that attributing the wood density effect to the growth-independent hazard term ($\gamma$; Fig. \ref{fig2} B). Specifically, we found that wood density was negatively correlated with a species' baseline mortality rate, $\gamma$ (Fig. \ref{fig3}). This meant that fast growing individuals from a low wood density species had, on average, higher mortality rates (Fig. \ref{fig4} A,B), and thus higher probability of death across a 1-yr period (Fig. \ref{fig4} C,D), relative to fast growing individuals of high wood density species. For example, a species with a wood density of 0.3 g $\textrm{cm}^{-3}$ had an estimated mean probability of dying of \Sexpr{round(extract_baseline_estimate(final_model,FALSE,0.3),2)['mean']} yr$^{-1}$ compared to \Sexpr{round(extract_baseline_estimate(final_model,FALSE,0.8),2)['mean']} yr$^{-1}$ for a species with a wood density of 0.8 g $\textrm{cm}^{-3}$. Incorporating an additional species-level random effect to capture any additional inter specific differences substantially improved model skill relative to a model with only wood density (Fig. \ref{fig2}A).

\begin{figure}[t]
\includegraphics{figures/fig4.pdf}
\caption{Predicted changes in instantaneous mortality rate (A,B), and 1-yr mortality probability (C,D), with increasing  growth rate. A,C) Estimated curves for all 203 BCI species used in this study. B,D) The average ($\pm$ 95\% credible intervals) curve for a high (0.8) and low (0.3) wood density species. See Figs. S3-S5 for species-level parameter estimates.}
\label{fig4}
\end{figure}

\subsection*{Proportion of variation explained}
To compliment the above analysis based on skill in predicting held-out data, we used the final fitted model to estimate the amount of variation captured by different factors in the predicted probability of dying across 1yr for all individuals (Fig. \ref{fig5}). Species-level effects contributed ~\Sexpr{extract_prop_explained(param_variance_explained, I('species'))}\% of predicted variation in 1-yr mortality. Wood density explained \Sexpr{extract_prop_explained(param_variance_explained, I('wood_density'))}\% of this species variation. Census accounted for only \Sexpr{extract_prop_explained(param_variance_explained, I('census'))}\% of the total predicted variation. The growth-dependent hazard (i.e. the part of the model allowed to vary by individual growth) accounted for \Sexpr{extract_prop_explained(param_variance_explained, I('growth_dependent'))}\% of the total variation, while growth-independent hazards accounted for the remainder (Fig. \ref{fig5}).

@@

\begin{figure}[t]
\includegraphics{figures/fig5.pdf}
\caption{Proportion of variation in predicted 1-year mortality (Fig. \ref{fig4}C) for all individuals captured by different effects. Effects are not mutually exclusive thus sum to more than 1.0. Note "wood density" is a subset of the overall "species" effect.}  
\label{fig5}
\end{figure}

@@

\begin{figure}[t]
\includegraphics{figures/fig6.pdf}
\caption{Posthoc correlations between estimated species parameters and measures of species light requirement (left) and species maximum DBH (right). Points are mean ($\pm$ 95\% credible intervals) for each of the 203 species used in this study. Blue line shows the average trendline as determined from standard linear regression. Gap index is a binary species level index of the light required for recruitment. Here low numbers indicate the species readily recruits under dense canopy and 1 indicates that a species only ever recruits in gaps.}
\label{fig6}
\end{figure}

@@

Eqs. \ref{eq:mortality_model}-\ref{eq:model} were fit to the data using Bayesian inference and with covariates for growth rate in previous census and wood density, as well as random effects. Growth rates were estimated from field measurements of diameter, which inevitably include observation error. In our dataset, \Sexpr{prop_neg_growth(BCI_model_dataset_true_dbh)}\% of estimated growth rates were negative. To ensure our mortality model was not biased by these unlikely values we first applied a probabilistic model to estimate \textit{``true growth''}, taking into account measurement error and the distribution of growth rate across the community (see Supplementary Material S1 for details; Fig. S1). The parameters $\alpha_s$, $\beta_s$ and $\gamma_s$ were modelled as a function of both wood density (measured at species level) and a species-level random effect:
\begin{equation}\label{eq:submodels}
\alpha_s = \alpha_{0,s} \, \left(\frac{\rho}{\rho_c}\right)^{\alpha_{1}},
\end{equation}
with similar formulations for $\beta_s$ and $\gamma_s$. Here $\alpha_{1}$ captures the effect of wood density $\rho$ on $\alpha_s$, while $\alpha_{0,s}$ captures any other species-level residual error not explained by wood density for species $s$, modelled as random realisations from log-normal distributions. The form of eq. \ref{eq:submodels} ensures that parameters remain positive; and on a log scale this equates to an additive linear model centered around $\rho_c$. We also centered growth rate $X_i$ at the lower 5\% quantile for both diameter increment and area growth (0.172 and 0.338, respectively), meaning $\alpha_s$ should be interpreted as the hazard rate when growth rate was very low. Weak priors on all hyper-parameters were set (see Supplementary Material S2 for details). Models were fit in R \Sexpr{paste(version$major, version$minor, sep='.')} using the package \texttt{rstan} \Sexpr{packageVersion("rstan")}\cite{StanDevelopmentTeam:2015uz} and employing some numerical optimisations (see Supplementary Material S3-S4 for details and example code). We executed three independent chains and in all cases modelled parameters converged within 2000 iterations. Convergence was assessed through both visual inspection of chains and reference to the Brooks-Gelman-Rubin convergence diagnostic \cite{Gelman:1992ts, Brooks:1998ju}. After discarding the first 2000 iterations as ‘burn in’, a further 2000 iterations were taken from the joint posterior. Species parameter estimates from the final model are shown in Figs. S3\textendash S5.

@@

\subsection*{Posthoc correlations}
We calculated a gap index as a measure of a species' light dependence using annual canopy census data collected during 1985\textendash1990 and 1990\textendash1995. The canopy census recorded, in all 5 by 5 m subplots across the 50 ha plot, the presence of leaf in six height intervals (0-2,2-5,5-10,10-20,20-30, \textgreater 30 m). For each subplot, we calculated the minimum number of strata > 2 m containing vegetation; and then transformed this to a light index ranging from 0 (dense shade) to 1 (gap). We then calculated a weighted sum for each subplot, using the values from the 8 neighbouring cells. The gap index for each species is then the average light level encountered by new saplings appearing in the census (Fig. S2).

@@

\acknow{We thank H. Muller-Landau and XX anonymous reviewers for feedback and B. Carpenter for technical advice.  We acknowledge S. Hubbell, R. Foster, R. Pérez, S. Aguilar, S. Lao, S. Dolins, \& hundreds of field workers for their contribution; and the National Science Foundation, Smithsonian Tropical Research Institute, \& MacArthur Foundation for funding the design, collection, quality control and management of long-term growth data at BCI. Fig. 1a uses images by Tracey Saxby, IAN Image Library. J.C., R.F., L.M. and D.S. were supported by the Science and Industry Endowment Fund (SIEF; RP04-174). D.F. and M.W. were supported by fellowships from the Australian Research Council.}

>>>>

\documentclass[9pt,twocolumn,twoside, lineno]{pnas-new}\usepackage[]{graphicx}\usepackage[]{color}

@@

Another difficulty when studying mortality -- similar to that faced in other fields like medicine and engineering -- is determining the shape of hazard functions that skilfully predict patterns in mortality. Past research has identified a range of factors with significant effects on tree survival, including an individual's growth rate \cite{Kobe:1995tw,Wyckoff:2002ul}, traits \cite{Poorter:2008iu,Kraft:2010kq,Wright:2010fl,AubryKientz:2013dg}, and size \cite{Vieilledent:2010fv}. However, these influences have not yet been integrated into a common hazard function \cite{Hawkes:2000ib,Zens:2003jv,McDowell:2011dr}.

@@

A further challenge in developing hazard functions for plants is to integrate the conflicting relationships observed within and across species between mortality and growth. Within species, mortality rates are lower for fast-growing individuals, presumably because those individuals have superior carbon budgets and are thus able to tolerate or repair diverse stresses \cite{Kobe:1995tw, Hawkes:2000ib, Keane:2001db}. Empirical studies broadly support this theory, with many indicating exponential declines in mortality with increased growth rate, $X_i(t)$ \cite{Kobe:1995tw, Wyckoff:2000un, Vieilledent:2010fv}. By contrast, across species, there is a strong trade-off between growth and survival, with individuals from faster-growing species  exhibiting higher mortality rates than individuals from slower-growing species \cite{Poorter:2008iu, Wright:2010fl}. This trade-off may arise via traits with antagonistic effects, such as wood density. Denser wood -- which is expensive to build and thus slows growth --  reduces stem breakage \cite{vanGelder:2006exa,Chave:2009iy}, embolism \cite{Hacke:2001kj, Jacobsen:2005fx}, pathogen attack \cite{Augspurger:1984wx}, and thereby mortality \cite{Poorter:2008iu, Chave:2009iy, Kraft:2010kq, Wright:2010fl}.

\begin{figure}[!hb]
\centering
\includegraphics{figures/fig1.pdf}
\caption{Outline of methodology.
A) Our data consist of repeat measures of stem diameter ($D$) and status ($S$, 0 = alive or 1 = dead) for individual trees at specific census dates ($t_1$, $t_2$, $t_3$).
B) We consider three alternative hazard functions: 1) a baseline hazard, 2) a growth-dependent hazard; and 3) a function that combines both baseline and growth-dependent hazards. The parameters of the models are biologically interpretable: $\alpha$ defines the instantaneous mortality rate at low growth rate; $\beta$ reflects the sensitivity of mortality rate to changes in growth rate; and $\gamma$ is the asymptote, or baseline hazard. Combined $\alpha$ and $\beta$ capture growth-dependent mortality, while $\gamma$ captures growth-independent mortality (e.g. windfall, fire) that kill a plant, irrespective of its growth rate. For each model form, we consider two alternative predictors of growth, $X$ (basal area and stem diameter growth), as well as allowing for species-level effects on the parameters $\alpha$, $\beta$ and $\gamma$.
C) Each model's skill in predicting observed outcomes ($S$) is quantified via the log-loss function (eq. \ref{eq:logloss}).
D) The predictive skill of alternative models was evaluated via 10-fold cross validation. The entire dataset is split into 10 folds ($F_1$, ..., $F_{10}$). Alternative models were fit 10 times ($M_1$, ..., $M_{10}$), using different combinations of testing (1 fold; orange) and training (9 folds; green) data. Predictive capacity was assessed by averaging the log loss's obtained from the 10 test data predictions.}
\label{fig1}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics{figures/fig2.pdf}
\caption{Predictive skill of alternative hazard functions. Values are mean ($\pm$ 95\% credible intervals) logarithmic loss, with lower values implying greater predictive skill.
A) Five sequential stages of model selection with each stage increasing in complexity. Null: constant ($\gamma$); Census: inclusion of census effects ($\delta_t$); Growth rate: the inclusion of growth rate. This includes two possible hazard functions: growth-dependent only hazard ($(\alpha e^{-\beta X_{i}})\delta_t$) and baseline + growth-dependent hazard with census effects ($(\alpha e^{-\beta X_{i}} + \gamma)\delta_t$); WD: inclusion of wood density effect ($\rho$) on $\gamma$; Species: the inclusion of species random effects $s$ on all parameters.
B) Predictive skill for wood density parameter combinations. Shading represent growth measure used: white = no growth measure, grey = basal area growth, black = dbh growth. For both panels symbols represent functional form: null (circle), growth-dependent hazard (triangle), both growth-independent and growth-dependent hazards (square).}
\label{fig2}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics{figures/fig3.pdf}
\caption{Relationship between species growth-independent mortality rate and wood density. Points are estimated mean baseline mortality rates $\pm$ 95\% credible intervals for each of the 203 BCI species used in this study. Blue trendline with grey shading shows average ($\pm$ 95\% credible intervals) expected relationship.}
\label{fig3}
\end{figure}

\subsection*{Wood density and other species effects}
Including wood density as an effect on either growth-independent or growth-dependent parameters significantly improved model skill relative to a model without such effects (Fig. \ref{fig2} A,B). The most parsimonious model, with highest predictive skill, was that attributing the wood density effect to the growth-independent hazard term ($\gamma$; Fig. \ref{fig2} B). Specifically, we found that wood density was negatively correlated with a species' baseline mortality rate, $\gamma$ (Fig. \ref{fig3}). This meant that fast growing individuals from a low wood density species had, on average, higher mortality rates (Fig. \ref{fig4} A,B), and thus higher probability of death across a 1-yr period (Fig. \ref{fig4} C,D), relative to fast growing individuals of high wood density species. For example, a species with a wood density of 0.3 g $\textrm{cm}^{-3}$ had an estimated mean probability of dying of \Sexpr{round(extract_baseline_estimate(final_model,FALSE,0.3),2)['mean']} yr$^{-1}$ compared to \Sexpr{round(extract_baseline_estimate(final_model,FALSE,0.8),2)['mean']} yr$^{-1}$ for a species with a wood density of 0.8 g $\textrm{cm}^{-3}$. Incorporating an additional species-level random effect to capture any additional inter specific differences substantially improved model skill relative to a model with only wood density (Fig. \ref{fig2}A). See Figs. S3-S5 for species-level parameter estimates.

\begin{figure}[t]
\includegraphics{figures/fig4.pdf}
\caption{Predicted changes in instantaneous mortality rate (A,B), and 1-yr mortality probability (C,D), with increasing growth rate. A,C) Estimated curves for all 203 BCI species used in this study. B,D) The average ($\pm$ 95\% credible intervals) curve for a high (0.8) and low (0.3) wood density species.}
\label{fig4}
\end{figure}

\subsection*{Proportion of variation explained}
To compliment the above analysis based on skill in predicting held-out (test) data, we used the final fitted model to estimate the amount of variation captured by different factors in the predicted probability of dying across 1yr for all individuals (Fig. \ref{fig5}). We achieved this by removing a parameter sequentially and calculating the proportion of the sum of squares attributed to a submodel relative to the full model. Species-level effects contributed ~\Sexpr{extract_prop_explained(param_variance_explained, I('species'))}\% of predicted variation in 1-yr mortality. Wood density explained \Sexpr{extract_prop_explained(param_variance_explained, I('wood_density'))}\% of this species variation. Census accounted for only \Sexpr{extract_prop_explained(param_variance_explained, I('census'))}\% of the total predicted variation. The growth-dependent hazard (i.e. the part of the model allowed to vary by individual growth) accounted for \Sexpr{extract_prop_explained(param_variance_explained, I('growth_dependent'))}\% of the total variation, while growth-independent hazards accounted for the remainder (Fig. \ref{fig5}).

@@

\begin{figure}[t]
\includegraphics{figures/fig5.pdf}
\caption{Proportion of variation in predicted 1-year mortality for all individuals captured by different effects. Effects are not mutually exclusive thus sum to more than 1.0. Note "wood density" is a subset of the overall "species" effect.}  
\label{fig5}
\end{figure}

@@

\begin{figure}[t]
\includegraphics{figures/fig6.pdf}
\caption{Posthoc correlations between estimated species parameters and measures of species light requirement (left) and species maximum DBH (right). Points are means ($\pm$ 95\% credible intervals) for each of the 203 species used in this study. Blue line shows the average trendline as determined from standard linear regression. Gap index is a species level index of the light required for recruitment. Low gap index indicates the species readily recruits under dense canopy and 1 indicates that a species only ever recruits in gaps.}
\label{fig6}
\end{figure}

@@

Eqs. \ref{eq:mortality_model}-\ref{eq:model} were fit to the data using Bayesian inference and with covariates for growth rate in previous census and wood density, as well as random effects. Growth rates were estimated from field measurements of diameter, which inevitably include observation error. In our dataset, \Sexpr{prop_neg_growth(BCI_model_dataset_true_dbh)}\% of estimated growth rates were negative. To ensure our mortality model was not biased by these unlikely values we first applied a probabilistic model to estimate \textit{``true growth''}, taking into account measurement error and the distribution of growth rate across the community (see Supplementary Material S1 for details; Fig. S1). The parameters $\alpha_s$, $\beta_s$ and $\gamma_s$ were modelled as a function of both wood density (measured at species level) and a species-level random effect:
\begin{equation}\label{eq:submodels}
\alpha_s = \alpha_{0,s} \, \left(\frac{\rho}{\rho_c}\right)^{\alpha_{1}},
\end{equation}
with similar formulations for $\beta_s$ and $\gamma_s$. Here $\alpha_{1}$ captures the effect of wood density $\rho$ on $\alpha_s$, while $\alpha_{0,s}$ captures any other species-level residual error not explained by wood density for species $s$, modelled as random realisations from log-normal distributions. The form of eq. \ref{eq:submodels} ensures that parameters remain positive; and on a log scale this equates to an additive linear model centered around $\rho_c$. We also centered growth rate $X_i$ at the lower 5\% quantile for both diameter increment and area growth (0.172 and 0.338, respectively), meaning $\alpha_s$ should be interpreted as the hazard rate when growth rate was very low. Weak priors on all hyper-parameters were set (see Supplementary Material S2 for details). Models were fit in R \Sexpr{paste(version$major, version$minor, sep='.')} using the package \texttt{rstan} \Sexpr{packageVersion("rstan")}\cite{StanDevelopmentTeam:2015uz} and employing some numerical optimisations (see Supplementary Material S3-S4 for details and example code). We executed three independent chains and in all cases modelled parameters converged within 2000 iterations. Convergence was assessed through both visual inspection of chains and reference to the Brooks-Gelman-Rubin convergence diagnostic \cite{Brooks:1998ju}. After discarding the first 2000 iterations as ‘burn in’, a further 2000 iterations were taken from the joint posterior. Species parameter estimates from the final model are shown in Figs. S3\textendash S5.

@@

\subsection*{Posthoc correlations}
We calculated a gap index as a measure of a species' light dependence using annual canopy census data collected during 1985\textendash1990 and 1990\textendash1995. The canopy census recorded, in all 5 by 5 m subplots across the 50 ha plot, the presence of leaf in six height intervals (0-2,2-5,5-10,10-20,20-30, \textgreater 30 m). For each subplot, we calculated the number of strata > 2 m containing vegetation; and then transformed this to a light index ranging from 0 (dense shade) to 1 (gap). As light may penetrate into a subplot from the edge of a subplot, we rescaled this index to account for values in the eight immediate neighbouring subplots. Specifically, we used a weighted sum approach whereby the central subplot is assigned a weight of 8 and the eight neighbouring subplots are assigned a weight of 1. This meant that the contribution of the central plot was equivalent to the combined effect of all eight neighbouring plots. These weighted values were then summed for each central cell and then these values were normalised to be between 0 and 1. The gap index for each species was then estimated as the average light level encountered by new saplings appearing in the census (Fig. S2).

@@

\acknow{We thank H. Muller-Landau and anonymous reviewers for feedback and B. Carpenter for technical advice. We acknowledge S. Hubbell, R. Foster, R. Pérez, S. Aguilar, S. Lao, S. Dolins, \& hundreds of field workers for their contribution; and the National Science Foundation, Smithsonian Tropical Research Institute, \& MacArthur Foundation for funding the design, collection, quality control and management of long-term growth data at BCI. Fig. 1a uses images by Tracey Saxby, IAN Image Library. J.C., R.F., L.M. and D.S. were supported by the Science and Industry Endowment Fund (SIEF; RP04-174). D.F. and M.W. were supported by fellowships from the Australian Research Council.}
